\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% Character encoding
\usepackage[utf8]{inputenc}

% Adjust the page margins for One Page Layout
\usepackage[scale=0.90, top=1.0cm, bottom=1.0cm]{geometry}
\recomputelengths

% Personal data
% UPDATED: Name is now a hyperlink to the personal website
\name{\href{https://welcome-makhubo.netlify.app}{Welcome}}{\href{https://welcome-makhubo.netlify.app}{Makhubo}}
\title{Final Year Student}
\address{7560 Bishop Street, Emaphupheni 1519}{South Africa}{}
\phone[mobile]{(+27)~78~365~0544}
\email{welcomemakhubo10@gmail.com}
% Hyperlinks for social profiles (Username only)
\social[github]{WelcomeLuu}
\social[linkedin]{welcome-makhubo-894534202}

%----------------------------------------------------------------------------------
%            CONTENT
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle
\vspace*{-10mm} % Tighten space after header

\section{Summary Profile}
\cvitem{}{Final Year Computer Science student specializing in Full-Stack Development and Business Analysis. Combines 3+ years of academic coding experience with strong leadership and stakeholder management skills. Highly self-motivated and committed to continuous upskilling through ongoing self-initiated projects.}

\section{Education}
\cventry{Feb 2023--Present}{BSc in Computer Science and Informatics}{University of Johannesburg}{}{}{}
\cventry{Feb 2018--Nov 2022}{National Senior Certificate}{Amos Maphanga Secondary School}{}{}{}

\section{Skills \& Competencies}
\cvitem{Languages}{Python, C\#, Java, C++, Visual Basic, SQL}
\cvitem{Frameworks}{ASP.NET, Django, React, Node.js, Bootstrap}
\cvitem{Core Skills}{Business Analysis, Stakeholder Management, Agile, Problem-Solving}

\section{Key Projects}
\cventry{2024}{Student Marketplace Platform}{Self-Initiated Project}{}{}{
\begin{itemize}
    \item Designed and developed a web-based marketplace for students using \textbf{ASP.NET}.
    \item Created a centralized platform allowing students to list, search, and exchange academic resources.
    \item Focused on backend logic and database integration to ensure reliable transaction handling.
\end{itemize}}

\section{Experience}
\cventry{Oct 2024--Present}{Student Life Intern (Leadership \& Analysis)}{Richmond Life}{}{}{
\begin{itemize}
    \item \textbf{Stakeholder Management:} Liaison between residence management and the student body.
    \item \textbf{Event Coordination:} Analyzed student needs to plan 10+ strategic events, balancing academic schedules with social well-being.
    \item \textbf{Crisis Management:} Mediated conflicts and provided support to residents.
\end{itemize}}

% Compacted entry to save space
\cventry{Nov 2022--Mar 2023}{Barman}{Catering Boys}{}{}{Provided high-quality service in VIP environments; ensured inventory accuracy and customer satisfaction.}

\section{Certifications}
\cventry{2025}{Certificate of Completion}{Financial Literacy}{Deloitte}{WorldClass Hub}{}
\cventry{2025}{Certificate of Completion}{Real-World Readiness}{Deloitte}{WorldClass Hub}{}
\cventry{2024}{Certificate of Completion}{Introduction to Blockchain, using Django}{UJBlockchain}{}{}
\cventry{2023}{Certificate of Completion}{Python and Problem-solving}{JBS}{}{Distinction}

\section{Languages}
\cvitem{}{Isizulu (Native), English (Professional), Sepedi (Conversational)}

\section{References}
\cventry{}{Available on Request}{}{}{}{}

\end{document}
